The sparseHessianFD package

### 2021-09-23 README.Rmd
set up pkgdown

---
title:  The sparseHessianFD package
output:
  md_document:
    variant: markdown_github
---

@@

# Why use the sparseHessianFD package?

@@

should suffice.  The package is being developed on github at
github.com/braunm/sparseHessian, and you can get development branches
there.

>>>>

---
title:  The sparseHessianFD package
output:
  md_document:
    variant: gfm
---

@@

# sparseHessianFD: Because gradients are easy, but Hessians are hard

@@

should suffice.  The package is being developed on [Github](www.github.com/braunm/sparseHessianFD), so you can also install from

```
devtools::install_github("braunm/sparseHessianFD")
```
